---
title: 'Chapter 5: Cochran''s  Q'
author: "Giulia Bertoldo"
date: "4/9/2022"
output: pdf_document
---

Based on the book "Doing Meta-analysis with R"

Random effect model, one equation:  

* $\widehat{\theta_j} = \widehat{\theta}  + u_j + r_j$

Random effect model, two equations: 

* $\widehat{\theta_j} = \theta_j + r_j$

* $\theta_j = \widehat{\theta}  + u_j$

Cochrane's Q:

* $Q = \sum_{k=1}^{K} w_k (\widehat{\theta_k} - \widehat{\theta})^2$


# Simulation

We want to inspect how Q behaves under two different scenarios: 

1. When there is no between-study heterogeneity  

2. When heterogeneity exists 

## Scenario 1: No between-study heterogeneity

In this case $u_j = 0$ and that the residuals $(\widehat{\theta_k} - \widehat{\theta})$ are only a product of the sampling error $r_j$.

We are going to draw a number of studies, for example $K = 40$, from a distribution. Because we assume no heterogeneity between studies (only sampling variance), the studies are drawn from the very same distribution. Here we model the deviations between a study's effect size and the overall effect size as a Standard Normal distribution (mean 0 and standard deviation 1): $(\widehat{\theta_k} - \widehat{\theta}) \sim N(0,1)$. 

```{r}
set.seed(123)
rnorm(n = 40, mean = 0, sd = 1)
```

Now let us repeat this process of drawing n=40 samples many, many times:

```{r}
set.seed(123)
error_fixed <- replicate(n=10000, rnorm(n = 40)) # rnorm is by default standard normal
```


## Scenario 2: There is between-study heterogeneity

We want to simulate the scenario where between-study heterogeneity ($u_j$ errors) esxists in addition to the sampling error ($r_j$). 

Let us assume that the true effect sizes of the studies have been sampled from a standard normal distribution. Because there is this added component of variability, we add an rnorm call to the previous code. 

```{r}
set.seed(123)
error_random <- replicate(n=10000, rnorm(n = 40) + rnorm(n = 40))
```

## Cochrane's Q

Here we are interested in evaluating the behavior of Q in the two scenarios. Then, we need to simulate many Q statistics for the scenario with heterogeneity and without heterogeneity. 

Assumption: to simplify, we assume that all studies have the same weight with value 1: $w_k = 1$.

```{r}
set.seed(123)
Q_fixed <- replicate(n=10000, sum(rnorm(n = 40)^2)) 
Q_random <- replicate(n=10000, sum((rnorm(n = 40) + rnorm(n = 40))^2))
```


Important: Q is assumed to follow a $\chi^2$ distribution with k-1 degrees of freedom **if effect size differences are only caused by sampling error**. So, the mean of the $\chi^2$ distribution with k-1 degrees of freedom tells us the value of Q that we expect through sampling error alone. 

```{r}
# Histogram of the residuals (theta_k - theta)
# - We produce a histogram for both the simulated values in
#   error_fixed and error_random
# - `lines` is used to add a normal distribution in blue.
hist(error_fixed, 
     xlab = expression(hat(theta[k])~-~hat(theta)), prob = TRUE, 
     breaks = 100, ylim = c(0, .45), xlim = c(-4,4),
     main = "No Heterogeneity")
lines(seq(-4, 4, 0.01), dnorm(seq(-4, 4, 0.01)), 
      col = "blue", lwd = 2)
hist(error_random, 
     xlab = expression(hat(theta[k])~-~hat(theta)), prob = TRUE, 
     breaks = 100,ylim = c(0, .45), xlim = c(-4,4),
     main = "Heterogeneity")
lines(seq(-4, 4, 0.01), dnorm(seq(-4, 4, 0.01)), 
      col = "blue", lwd = 2)
```

When there is no heterogeneity the 'residuals' $(\widehat{\theta_k} - \widehat{\theta})$ follow a standard normal distribution (because that is the distribution we used to generate the data). 

When there is heterogeneity the distribution departs from the standard normal.

```{r}
# Histogram of simulated Q-values
# - We produce a histogram for both the simulated values in
#   Q_fixed and Q_random
# - `lines` is used to add a chi-squared distribution in blue.
# First, we calculate the degrees of freedom (k-1)
# remember: k=40 studies were used for each simulation
df <- 40-1
hist(Q_fixed, xlab = expression(italic("Q")), prob = TRUE, 
     breaks = 100, ylim = c(0, .06),xlim = c(0,160),
     main = "No Heterogeneity")
lines(seq(0, 100, 0.01), dchisq(seq(0, 100, 0.01), df = df), 
      col = "blue", lwd = 2)
hist(Q_random,  xlab = expression(italic("Q")), prob = TRUE, 
     breaks = 100, ylim = c(0, .06), xlim = c(0,160),
     main = "Heterogeneity")
lines(seq(0, 100, 0.01), dchisq(seq(0, 100, 0.01), df = df), 
      col = "blue", lwd = 2)
```

If we have no heterogeneity, the distribution of Q values follows a Chi-Square distribution with k-1 degrees of freedom. In this case variation in the observed effect sizes exists only because of sampling error.  

If we do have heterogeneity, Q departs from the Chi-Square distribution with k-1 degrees of freedom. The variation that we observed is not due to sampling error alone.  

