---
title: "Meta-analysis based on Sisks et al. (2018) - V.2"
author: "Giulia Bertoldo"
date: "4/10/2022"
output: 
  pdf_document:
    toc: true 
---

# Packages and Data

```{r}
# Load packages
library(tidyverse)
library(meta)
library(metafor)
library(readxl)
library(gridExtra) # for arranging qqplots
library(multcomp) # for multiple comparisons

# Import data
df1 <- read_excel('data/mindset.xlsx', sheet = 'Meta-analysis 1')
```

```{r}
# FUNCTION TO CALCULATE I^2 FOR EACH LEVEL IN A 3-LEVEL MODEL

# Formulae 4.29 Chen 2015 + Paper
# Higgins and Thompson (2002) preferred to define the typical within-study
# sampling variance ... using the Q statistic:


# Inputs:
# v: variance (e.g. df$vi)
# k: number of studies (e.g. length(df$vi))
# rma_obj: meta-analysis object (e.g. multilevel1)

multilevel_i2 <- function(v, k, rma_obj)
{
  k <- length(v)
  list.inverse.variances <- 1 /(v)
  sum.inverse.variances <- sum(list.inverse.variances)
  numerator <- (k - 1) * sum.inverse.variances

  squared.sum.inverse.variances <- (sum.inverse.variances)^2

  list.inverse.variances.square <- 1 / (v^2)
  sum.inverse.variances.square <- sum(list.inverse.variances.square)
  denominator <- squared.sum.inverse.variances - sum.inverse.variances.square

  estimated.sampling.variance <- numerator / denominator

  I2_1 <- (estimated.sampling.variance) / (rma_obj$sigma2[1] + rma_obj$sigma2[2] + estimated.sampling.variance)

  I2_2 <- (rma_obj$sigma2[1]) / (rma_obj$sigma2[1] + rma_obj$sigma2[2] + estimated.sampling.variance)

  I2_3 <- (rma_obj$sigma2[2]) / (rma_obj$sigma2[1] + rma_obj$sigma2[2] + estimated.sampling.variance)

  I2_1 <- round((amountvariancelevel1 <- I2_1 * 100),2)
  I2_2 <- round((amountvariancelevel2 <- I2_2 * 100),2)
  I2_3 <- round((amountvariancelevel3 <- I2_3 * 100),2)

  col1 <- rbind(I2_1, I2_2, I2_3)
  col2 <- rbind('Level 1', 'Level 2', 'Level 3')
  I2_partition <- data.frame(col1, col2)
  names(I2_partition) <- c('I2', 'Level')
  print(I2_partition)

  # Barplot
  ggplot(I2_partition, aes(x="", y=I2, fill=Level))+
    geom_bar(width = 1, stat = "identity") +
    theme_light()

}
```

\newpage

# Data cleaning 

```{r}
# Glimpse data
glimpse(df1)
```

```{r}
# Rename columns
df2 <- rename(df1, 
             document_id = 'Document #', 
             study_id = 'Study #',
             sample_id = 'Sample #',
             sample_country = 'Sample Country',
             es_id = 'ES #',
             reference = 'Reference', 
             n = N, 
             adjusted_n = 'Adjusted N', 
             student_description = 'Student Description', 
             school_level = 'School Level', 
             development_stage = 'Development Stage', 
             risk_status = 'Risk status', 
             ses = SES, 
             ms_measure = 'MS Measure', 
             ms_measure_description = 'MS Measure Description', 
             mindset_type = 'Mindset Type', 
             achievement_measure_description = 'Achievement Measure Description', 
             academic_achievement_measure_type = 'Academic Achievement Measure Type',
             lab_based = 'Lab-based', 
             published = 'Published',
             es_type = 'ES type', 
             calculation = 'Calculation', 
             variance = 'Variance', 
             adjusted_variance = 'Adjusted Variance', 
             is_significant = 'Significant?', 
             growth_m = 'Growth M',
             growth_sd = 'Growth SD',
             other_m = 'Other M', 
             other_sd = 'Other SD', 
             cohen_d = "Cohen's d",
             calculated_r = 'Calculated r', 
             notes = Notes)
         

# Check that variable types is correct
glimpse(df2)

```

```{r}
# Change school_level from character to factor 
df2$school_level <- as.factor(df2$school_level)
levels(df2$school_level)

# Change development_stage from character to factor
df2$development_stage <- as.factor(df2$development_stage)
levels(df2$development_stage)
# Convert all "Wide range" level to "Wide Range"
df2$development_stage <- recode_factor(df2$development_stage, 
                                       'Wide range' = 'Wide Range')
levels(df2$development_stage)

# Change risk_status from character to factor
df2$risk_status <- as.factor(df2$risk_status)
levels(df2$risk_status)
## Note: The category '.' applies to 4 rows 
## These are studies from which it was not possible to determine the risk status
## df2 %>% 
##   filter(risk_status == '.')

# Change ses from character to factor
df2$ses <- as.factor(df2$ses)
levels(df2$ses)

# Change mindset_type from character to factor
df2$mindset_type <- as.factor(df2$mindset_type)
levels(df2$mindset_type)

# Change academic_achievement_measure_type from character to factor
df2$academic_achievement_measure_type <- as.factor(df2$academic_achievement_measure_type)
levels(df2$academic_achievement_measure_type)

# Change lab_based from character to factor
df2$lab_based <- as.factor(df2$lab_based)
levels(df2$lab_based)

# Change published from character to factor
df2$published <- as.factor(df2$published)
levels(df2$published)

# Change es_type from character to factor
df2$es_type <- as.factor(df2$es_type)
levels(df2$es_type)

# Change is_significant from character to factor
df2$is_significant <- as.factor(df2$is_significant)
levels(df2$is_significant)
```

```{r}
# Create dataframe for metafor: 
# Calculate r-to-z transformed correlations and corresponding sampling variances
df3 <- escalc(measure="ZCOR", ri=r, ni=n, data=df2)
```

```{r}
# Explore graphically Fisher's Z
ggplot(df3, aes(x=yi)) +
  geom_histogram(aes(y=..density..), colour = 'black', fill = "white") +
  geom_density(alpha=.2, fill="#FF6666") +
  theme_classic()

# Fisher's Z
qqplot_z <- ggplot(df3, aes(sample=yi)) +
  stat_qq() +
  stat_qq_line() +
  theme_classic()

# Original r 
qqplot_r <- ggplot(df3, aes(sample=r))+
  stat_qq() +
  stat_qq_line() +
  theme_classic()

grid.arrange(qqplot_r, qqplot_z, ncol=2)
```
\newpage 

# Meta-analysis 1: Random-effects model (REM)

Other notes: REML to estimate tau, no hakn correction.

```{r}
# REM of the transformed correlations 
meta1 <- rma (yi = yi, 
                  vi = vi,
                  measure = 'ZCOR',
                  data = df3, 
                  slab = es_id)
summary(meta1, digits = 3)
```

## Pooled effect size 

* Number of studies = 273 

* estimate = 0.1071, with 95% CI [0.0869, 0.1272], z = 10.4110 and p-value <.0001. However, this Fisher's z, so, we need to transform it back to Pearson r for interpretation

```{r}
# Transform from z to r and see if the values you obtain make sense: 
transf.ztor(0.1071)
transf.ztor(0.0869)
transf.ztor(0.1272)

# From examples: https://wviechtb.github.io/metadat/reference/dat.molloy2014.html
# Documentation: predict.rma
## returns the estimated (average) outcome in the hypothetical population of studies from which the set of studies are assumed to a random selection. Same estimate of the intercepet in REM.
predict(meta1, digits=3, transf=transf.ztor)
```

* estimate = 0.107, with 95% CI [0.087, 0.127] 

* The prediction interval ranges is $r = [-0.161, 0.359]$ . This means that it is possible that some future studies will find a negative correlation between mindset and academic achievement based on the present evidence. But the interval spans also over to a substantial positive effect. 

\newpage

### Analysis of between-studies heterogeneity

* Cochrane's Q: If there was no heterogeneity this statistics should be distributed as a $\chi^2$ distribution with 272 degrees of freedom. In our meta-analysis $Q = 8958.24$  with p < .0001. We reject the null hypothesis of homogeneity. There is evidence for heterogeneity. 

```{r}
# Obtain confidence interval for tau^2, I^2, H
# Interval for tau^2 is obtained iteratively either via the Q-profile method or via the generalized Q-statistic method
# The square root of the inter- val bounds is also returned for easier interpretation.
# Confidence intervals for I2 and H2 are also provided (Higgins & Thompson, 2002). Since I2 and H2 are just monotonic transfor- mations of tau2 the confidence intervals for I2 and H2 are also exact
confint.rma.uni(meta1, digits = 3)

```
* $I^2 = 95.68%$ (95%CI:95.08 - 97.10%), meaning that about 96% of the variability in effect sizes is due between-study heterogeneity. This can be considered substantial heterogeneity (according to Thomppson's rule of thumb).

* H^2 is 23.13. Values greater than 1 indicate heterogeneity.

* $\tau^2$, the between-study variance, is 0.0187 with 95% confidence interval [0.016, 0.0284], which does not include zero. Indicates heterogeneity. The confidence interval for $\tau^2$ was calculated based on the Q-profile method or the generalized Q-statistic method.

* $\tau$, is the 'standard deviation of the true effect size and [...] it tells us something about the range of the true effect sizes. The true effect sizes have an estimated standard deviation of $SD = 0.1369$ expressed on the scale of (**Question: Pearson correlation or Fisher's Z?)**

\newpage

## Forest plot 

```{r}
pdf(file='forestplot_metafor.pdf', width = 8, height = 30)
forest(meta1,
       header = TRUE, 
       transf = transf.ztor,
       showweights = TRUE, 
       order = 'obs',
       efac = 0.2)

### add text with Q-value, dfs, p-value, and I^2 statistic
# https://www.metafor-project.org/doku.php/plots:forest_plot
text(-4.6, -3, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(meta1$QE, digits=2, format="f")), ", df = ", .(meta1$k - meta1$p),
     ", p = ", .(formatC(meta1$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(meta1$I2, digits=1, format="f")), "%)")))
dev.off()

```

Notes: 

* Many of the more precise studies (smaller confidence interval), have an average correlation between -0.03 and 0.24

\newpage

## Caterpillar plot 

```{r}
# Source code:
# http://www.metafor-project.org/doku.php/plots:caterpillar_plot 
### create plot
forest(df3$yi, df3$vi,
       xlim=c(-2.5,3.5),        ### adjust horizontal plot region limits
       order="obs",             ### order by size of yi
       slab=NA, annotate=FALSE, ### remove study labels and annotations
       efac=0,                  ### remove vertical bars at end of CIs
       pch=19,                  ### changing point symbol to filled circle
       col="gray40",            ### change color of points/CIs
       psize=2,                 ### increase point size
       cex.lab=1, cex.axis=1,   ### increase size of x-axis title/labels
       lty=c("solid","blank"),  ### remove horizontal line at top of plot
       transf = transf.ztor)  
 
### draw points one more time to make them easier to see
points(sort(df3$yi), length(df3$vi):1, pch=19, cex=0.5)
 
### add summary polygon at bottom and text
addpoly(meta1, mlab="", cex=1, col = 'red')
text(-2, -2, "RE Model", pos=4, offset=0, cex=1)
```

\newpage

## Outliers and Influential cases

```{r}
inf <- influence(meta1)
pdf(file='infleunce.pdf')
plot(inf)
dev.off()
```

```{r}
### create Baujat plot
baujat(meta1, symbol="slab")
```
```{r}
# Look at es_id = 9 and 187
df3  %>% filter(es_id == 9) 
```

\newpage

## Subgroup analysis 

Sisks et al. (2018) found as **significant** moderators: 

* Student factors:
    + Developmental stage of the student: children, adolescents, adults

* Developmental stage as a moderator of mind-set on GPA 

Sisks et al. (2018) found as **non- significant** moderators: 

* Student factors:
    + Academic risk status: low-risk, moderately at risk, highly at-risk students
    + Socioeconomic status 

* Academic achievement measure: Course exam, Course grade, GPA, Standardized test  

### Developmental stage
```{r}
# Prepare dataset
levels(df3$development_stage)
# Subset to exclude "Wide Range" 
df3_develop <- filter(df3, 
                      (development_stage == "Adolescents") | 
                        (development_stage == "Adults") |
                        (development_stage == "Children"))
# Adjust labels
df3_develop$development_stage <- droplevels(df3_develop$development_stage)
levels(df3_develop$development_stage)
```

```{r}
# Inspect visually the relationship between Fisher's z and the categories 
# x = developmental_stage y = Fisher's z 
ggplot(data=df3_develop, mapping = aes(x=development_stage, y = yi)) +
  geom_dotplot(binaxis='y', 
               stackdir='center', 
               stackratio=1.5, 
               dotsize=0.5,
               fill="#3399ff") +
  stat_summary(fun.y=mean, geom="point", shape=18,
                 size=3, color="#ff5050")+
  theme_classic()

```

We see overlap in the outcome between the three categories, though it may be that children and adolescents show a higher effect than adults. 

The range of values is larger for adolescents and children compared to adults. Probably this would call for estimating different tau^2 for each group 

Next, I a weighted ANOVA. There are two options: 

* common $\tau^2$: 

* different $\tau^2$


```{r}
# Fit meta-analysis: 
# COMMON TAU^2: 
## Same between-study variance within each subgroup (Adolescents, Adults, Children)
meta1_develop1 <- rma (yi = yi,
                      vi = vi,
                      measure = 'ZCOR',
                      data = df3_develop,
                      mods = ~ development_stage-1)
summary(meta1_develop1, digits = 3)

# Transform the estimates of the differences from z to r 
transf.ztor(meta1_develop1$b)

# Multiple comparisons
# https://wviechtb.github.io/metafor/reference/rma.uni.html
multcomp_develop1 <- glht(meta1_develop1,
                         linfct=contrMat(c("Adolescents"=1,"Adults"=1,"Children"=1),
                                         type="Tukey"),test=adjusted("bonferroni"))

summary(multcomp_develop1)
# Note that the estimate of the differences in the output are Fisher z
```

```{r}
# Fit meta-analysis: 
# DIFFERENT TAU^2 PER SUBGROUP: 
## Different between-study variance within each subgroup (Adolescents, Adults, Children)
# https://wviechtb.github.io/metafor/reference/rma.uni.html

# We have to fit 3 models: ado, adu, chi
meta1_develop2_ado <- rma (yi = yi,
                           vi = vi,
                          measure = 'ZCOR',
                          data = df3_develop,
                          mods = ~ development_stage-1,
                          subset = (development_stage=="Adolescents")) 
summary(meta1_develop2_ado, digits = 3)

meta1_develop2_adu <- rma (yi = yi,
                           vi = vi,
                          measure = 'ZCOR',
                          data = df3_develop,
                          mods = ~ development_stage-1,
                          subset = (development_stage=="Adults")) 
summary(meta1_develop2_adu,  digits = 3)

meta1_develop2_chi <- rma (yi = yi,
                           vi = vi,
                          measure = 'ZCOR',
                          data = df3_develop,
                          mods = ~ development_stage-1,
                          subset = (development_stage=="Children")) 
summary(meta1_develop2_chi, digits =3)

# Compare tau^2 
tau2_comp <- data.frame(rbind(meta1_develop1$tau2, 
                        meta1_develop2_ado$tau2,
                        meta1_develop2_adu$tau2,
                        meta1_develop2_chi$tau2))
names(tau2_comp) <- 'tau^2'
rownames(tau2_comp) <- c('Common', 'Adolescents', 'Adults', 'Children')
round(tau2_comp, 3)

# Compare I^2
i2_comp <- data.frame(rbind(meta1_develop1$I2, 
                        meta1_develop2_ado$I2,
                        meta1_develop2_adu$I2,
                        meta1_develop2_chi$I2))
names(i2_comp) <- 'I^2'
rownames(i2_comp) <- c('Common', 'Adolescents', 'Adults', 'Children')
round(i2_comp,2)
```
\newpage

## Multilevel meta-analysis 

```{r}
meta1_multi1 <- rma.mv(yi = yi, 
                      V = vi, 
                      random = list(~1 | study_id/es_id), 
                      data = df3,
                      slab = es_id)

# QUESTION: I don't have to specify  measure = 'ZCOR'?

summary(meta1_multi1, digits =3)
```
* Variance components: 
    + The between-study variance is sigma^2.1 = 0.0153 (equivalent to tau^2 in REM)- At this level we have 129 studies. 
    + The within-study variance is sigma^2.2 = 0.0041. At this level we have 273 effect sizes. 

* Estimate: 0.0906. However, this is a Fisher's z, so we have to transform the effect back to a normal correlation: 

```{r}
round(transf.ztor(meta1_multi1$b), 3)
round(transf.ztor(meta1_multi1$ci.lb), 3)
round(transf.ztor(meta1_multi1$ci.ub), 3)
```
* The correlation is approximately 0.09 with 95%CI [0.065,0.116] 

* The test for heterogeneity rejects the null hypothesis of homogeneity, "however this is not informative. Instead, we should look at the amount of heterogeneity caputred by each level in our model." "We are interested in within-study variance (level 2) as well as between-study variance (level 3) and not the variance between all effect sizes in the dataset". 

### Testing the within-study variance

```{r}
# Two-level model without within-study variance 

meta1_multi2 <- rma.mv(yi = yi, 
                      V = vi, 
                      random = list(~1 | study_id/es_id), 
                      data = df3,
                      slab = es_id,
                      sigma2 = c(0, NA))

# Perform a likelihood-ratio test to determine the significance of 
# the within-study variance
anova(meta1_multi1, meta1_multi2)

```

* From the LRT we "found significant variability between effect-sizes within studies"

### Testing the between-study variance


```{r}
# Two-level model without between-study variance 

meta1_multi3 <- rma.mv(yi = yi, 
                      V = vi, 
                      random = list(~1 | study_id/es_id), 
                      data = df3,
                      slab = es_id,
                      sigma2 = c(NA, 0))

# Perform a likelihood-ratio test to determine the significance of 
# the within-study variance
anova(meta1_multi1, meta1_multi3)

```

* "Between-study variance is significant, since the fit of the full model is significantly better than the fit of the reduced model". "We found significant variability between studies"

* However, we would like to know how the total variance is splitted in the different levels. See next section

### Distribution of variance over the three levels of the meta-analytic model 

```{r}
# I^2 at different levels
# See function description under 'Packages and data' at the top
multilevel_i2(v = df3$vi, 
              k = length(df3$vi),
              rma_obj = meta1_multi1)
```
* Chen, 2015 pg. 92:  "I2 can be interpreted as the proportion of the total variation of the effect size that is due to the between-study heterogeneity"

* 4.17 % of the total variance can be attributed to within-study sampling variance (level-1)

* 75.43 % of the total variance can be attributed to within study variance  (differences between effect sizes within studies)

* 20.4 % of the total variance can be attributed to differences between studies at level 3. 

Conclusion: A lot of the variance is within-studies 

### Subgroup analysis 

#### Developmental stage

```{r}
# Fit 3-level model with developmental_stage as moderator

meta1_multi1_develop1 <- rma.mv(yi = yi, 
                                V = vi,
                                random = list(~1 | study_id/es_id),
                                data = df3_develop,
                                slab = es_id,
                                mods = ~ development_stage -1)

# QUESTION: I don't have to specify  measure = 'ZCOR'?
summary(meta1_multi1_develop1, digits =3)

# Multiple comparisons
multcomp_multi1_develop1 <- glht(meta1_multi1_develop1,
                                 linfct=contrMat(c("Adolescents"=1,"Adults"=1,"Children"=1),
                                         type="Tukey"),test=adjusted("bonferroni"))

summary(multcomp_multi1_develop1)
# Note that the estimate of the differences in the output are Fisher z
```

* Test for residual heterogeneity is significant: there is  significant unexplained variance left between all effect sizes in the data set after publication status has been added to the meta-analytic model 

* Test of moderators: Omnibus test. We reject the null hypothesis of no moderation ?
Developmental stage is a moderator

* Effects: Adolescents and children significantly different from zero, adults no. 

#####  Examine the residual within-study and between-study variance 

```{r}
multilevel_i2(df3_develop$vi, 
              k = length(df3_develop$vi),
              rma_obj = meta1_multi1_develop1)

```

## Publication bias

### Funnel plot 

```{r}
# Reference: https://wviechtb.github.io/metafor/reference/funnel.html 
funnel(meta1, 
       level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       legend=TRUE)
```

### Egger's regression test

```{r}
# Reference: https://wviechtb.github.io/metafor/reference/regtest.html
regtest(meta1, model = 'lm')
```

We cannot reject the null hypothesis that the intercept is equal to zero. Therefore we do not have evidence for funnel plot asymmetry. ("When there is no publication bias, the expected z score should be scattered around zero. No publication bias means means that the precision is not related to the effect size reported (beta1=0)).

```{r}
# Manually do calculations 
df3 %>%
  mutate(inv_se = 1/sqrt(vi)) %>%
  lm(yi ~ inv_se, data =.) %>%
  summary()
```

```{r}
# Plot precision vs effect size
df3 %>%
  mutate(inv_se = 1/sqrt(vi)) %>%
  ggplot(mapping = aes(x = inv_se, y =yi)) +
  geom_point() +
  geom_abline() +
  theme_light()
```

```{r}
# Check with meta
library(meta)
meta_del <- metacor(cor = r, 
                 n = n, 
                 studlab = reference, 
                 data= df2, 
                 fixed = FALSE, 
                 random = TRUE, 
                 method.tau = 'REML', 
                 hakn = FALSE, 
                 title = "Mindset and Academic Achievement", 
                 prediction = TRUE)
metabias(meta_del, method.bias = 'linreg')
```

### Trim and Fill method

```{r}
# Reference: 
meta1_tf <- trimfill(meta1)
summary(meta1_tf)
funnel(meta1_tf, legend=TRUE, cex=1.2)
```
\newpage

### Selection models 

#### Three-parameter selection model

```{r}
meta1_3psm1 <- selmodel(meta1,
                       type = 'stepfun', 
                       steps = 0.025)
summary(meta1_3psm1)
```

```{r}
meta1_3psm2 <- selmodel(meta1,
                       type = 'stepfun', 
                       steps = 0.05)
summary(meta1_3psm2)
```
